### 2016-07-01 FS4/STO1/sto1_heft.tex
12.2.a

% import math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% contradiction lightning
\usepackage{stmaryrd}
% better tilde
\usepackage{textcomp}
% algorithms and pseudo code
\usepackage{algorithmic}
\usepackage{algorithm}
%\usepackage{clrscode3e}
% formatting and layout
\usepackage{color}
\usepackage{fancyhdr}
% references and links
\usepackage{hyperref}
\usepackage{lastpage}
% settings
\usepackage{perpage}
\MakePerPage{footnote}
% custom text colors
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
% tikz
\usepackage{tikz}
\usetikzlibrary{%
	arrows,			% arrow types
	automata,		% states and transitions
	positioning,	% position shifting
	shapes,			% circles and stuff for Venn diagrams
	backgrounds		% coloring and stuff
}
\usepackage{pgf}

@@

%%%%%	a
\sss

>>>>

% import math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
% contradiction lightning
\usepackage{stmaryrd}
% better tilde
\usepackage{textcomp}
% algorithms and pseudo code
\usepackage{algorithmic}
\usepackage{algorithm}
%\usepackage{clrscode3e}
% formatting and layout
\usepackage{color}
\usepackage{fancyhdr}
% references and links
\usepackage{hyperref}
\usepackage{lastpage}
% settings
\usepackage{perpage}
\MakePerPage{footnote}
% custom text colors
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
% tikz
\usepackage{tikz}
\usetikzlibrary{%
	arrows,			% arrow types
	automata,		% states and transitions
	positioning,	% position shifting
	shapes,			% circles and stuff for Venn diagrams
	backgrounds		% coloring and stuff
}
\usepackage{pgf}
\usepackage{pgfplots}

@@

%%%%%	a
\sss
\[
    \begin{array}{rll|l||rll|l}
    0&\leq&\gamma x&&0&\leq&\gamma(2-x)&\\
    \frac{0}{x}&\leq&\gamma&\text{Fall 1: }1\geq x>0&\frac{0}{2-x}&\leq&\gamma&\text{Fall 1: }1\leq x<2\\
    0&\leq&\gamma&&0&\leq&\gamma&\\
    \frac{0}{x}&\leq&\gamma&\text{Fall 2: }x=0&\frac{0}{2-x}&\leq&\gamma&\text{Fall 2: }x=2\\
    0&\leq&\gamma 0&&0&\leq&\gamma(2-2)&\\
    0&\leq&0&&0&\leq&\gamma0&\\
    &&&&0&\leq&0&\\
    \end{array}
\]
$\Rightarrow \gamma$ darf beliebig größergleich $0$ gewählt werden.\\
\\
\[
    \begin{array}{rlll}
        \int_{-\infty}^{\infty}f(x)&=&\int_{-\infty}^{0}0~dx+\int_{0}^{1}\gamma x~dx+\int_{1}^{2}\gamma(2-x)~dx+\int_{2}^{\infty}0~dx&\\
        &=&0+\int_{0}^{1}\gamma x~dx+\int_{1}^{2}\gamma(2-x)~dx+0&\\
        &=&\int_{0}^{1}\gamma x~dx+\int_{1}^{2}2\gamma-2x~dx&\\
        &=&\left[\frac{\gamma}{2} x^2\right]_0^1+\left[2\gamma x -x^2\right]_{1}^{2}&\\
        &=&\frac{\gamma}{2}1^2-\frac{\gamma}{2}0^2+2\gamma 2 -2^2-2\gamma 1 -1^2&\\
        &=&0.5\gamma-0+4\gamma-4-2\gamma-1&\\
        &=&2.5\gamma-5&\\
    \end{array}
\]
Damit $f(x)$ eine Dichte wird muss $1$ herauskommen:
\[
    \begin{array}{rlll}
        1&=&2.5\gamma-5&\text{\textbackslash $+5$}\\
        6&=&2.5\gamma&\text{\textbackslash $:2.5$}\\
        2.4&=&\gamma&
    \end{array}
\]
Somit ist $\gamma=2.4$.\\
Für die Skizze siehe Abbildung \ref{12.2.a}

\begin{figure}
\begin{tikzpicture}[domain=-1:3]
    \draw[very thin,color=gray] (-1.1,-0.1) grid (3.1,3.1);
    \draw[->] (-1.2,0) -- (3.2,0) node[right] {$x$}; \draw[->] (0,-0.2) -- (0,3.2) node[above] {$f(x)$};
    \draw[color=blue, samples=150, domain=-1:0]   plot (\x,{0})   node[right] {};
    \draw[color=blue, samples=150, domain=0:1]   plot (\x,{2.4*\x})   node[right] {};
    \draw[color=blue, samples=150, domain=1:2]   plot (\x,{2.4*(2-\x)})   node[right] {};
    \draw[color=blue, samples=150, domain=2:3]   plot (\x,{0})   node[right] {};
    %\begin{axis}
    %\addplot[color=red, domain=0:4] {1.3*ln(x+1)};
    %\addplot[color=blue, domain=-1:1] {x};
    %\end{axis}
\end{tikzpicture}
\caption{f(x) für $x\in[-1,3]$}
\label{12.2.a}
\end{figure}
%%%%%	b
\sss
